---
title: "Case Study"
author: Minjie Bao
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup,include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() +  theme(legend.position = "bottom"))

options(
  ggplots2.continuous.color = "viridis",
  ggplots2.continuous.fill = "viridus"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## load the airbnb data
```{r}
data("nyc_airbnb")
## nyc_airbnb %>% slice(1:1000)
## nyc_airbnb %>% sample_n(1000)
## nyc_airbnb %>% sample_frac(size = .1)
```

## Brainstorm some questions

* what is the best Airbnb in staten island for <$100
* what price range is popular in each borough? most rented?
* what apartment features are related to price?
* cheapest room type in each neighborhood?
* hosts have higher ratings?


## data cleaning
```{r}
nyc_airbnb =
nyc_airbnb %>% 
  mutate(stars = review_scores_location/2) 

```

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(names_from = room_type, values_from = n)
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarise(mean_price = mean(price))
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(price < 1000, neighbourhood_group == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x=neighbourhood, y=price)) +
  geom_boxplot() +
  coord_flip()
```

```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x=lat, y = long, color = price)) +
  geom_point()
```

## Create a leaflet map
```{r}
pal <- colorNumeric("magma", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  drop_na(stars) %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color =~ pal(stars))
```

